### 2012-07-24 docs/mg/mg.tex
information about the mg_tower

@@

@@

>>>>

The following parameters are specified when building the \mgtower:
\begin{itemize}
\item {\tt smoother}: the type of smoother to use.  Choices are listed
  in {\tt mg\_tower.f90}.  Common options are {\tt
    MG\_SMOOTHER\_GS\_RB} for red-black Gauss-Seidel and {\tt
    MG\_SMOOTHER\_JACOBI} for Jacobi.

\item {\tt nu1}: The number of smoothings at each level on the way down
  the V-cycle.

\item {\tt nu2}: The number of smoothings at each level on the way up
  the V-cycle.

\item {\tt nub}: The number of smoothing before and after the bottom solver.

\item {\tt gamma}: \MarginPar{what does this mean?}

\item {\tt cycle\_type}: The type of multigrid to do, V-cycles ({\tt
  MG\_VCycle}), W-cycles ({\tt MG\_WCycle}), full multigrid ({\tt
  MG\_FCycle}).

\item {\tt omega}:  \MarginPar{description?}

\item {\tt bottom\_solver}: the type of bottom solver to use.  See the next
 section.

\item {\tt bottom\_max\_iter}: the maximum number of iterations for the 
  bottom solver

\item {\tt bottom\_solver\_eps}: the tolerance used by the bottom
  solver.  In \maestro, this is set via {\tt mg\_eps\_module}.

\item {\tt max\_iter}: the maximum number of multigrid cycles.

\item {\tt max\_bottom\_nlevel}: additional coarsening if you use
  {\tt bottom\_solver} type 4 (see below)

\item {\tt min\_width}: minimum size of grid at coarsest multigrid level

\item {\tt rel\_solver\_eps}: the relative tolerance of the solver (in
  \maestro, this is set via {\tt mg\_eps\_module}.

\item {\tt abs\_solver\_eps}: the absolute tolerance of the solver (in
  \maestro, this is set via {\tt mg\_eps\_module}.

\item {\tt verbose}: the verbosity of the multigrid solver.  In \maestro,
  this is set via the {\tt mg\_verbose} runtime parameter.  Higher
  numbers give more verbosity.

\item {\tt cg\_verbose}: the verbosity of the bottom solver.  In \maestro,
  this is set via the {\tt cg\_verbose} runtime parameter.  Higher
  numbers give more verbosity.

@@

All \maestro\ multigrid solves consist of pure V-cycles.

@@

\section{General Remarks}

If \maestro\ has trouble converging in the multigrid solves, try
setting the verbosity {\tt mg\_verbose} or {\tt cg\_verbose} to
higher values to get more information about the solve.
